The low-frequency environment of the Murchison Widefield Array: radio-frequency interference analysis and mitigation

### 2014-11-18 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Abraham's comments

The poly-phase filter bank that performs the first separation into sub-bands, introduces a 1.28~MHz periodic spectral signature, which is shown in Fig.~\ref{fig:bandpass}. The poly-phase filter band-pass shape is hard to remove completely, because the filters are imperfect and each sub-band is affected by leakage from signals in its adjacent sub-bands. The leakage from adjacent sub-bands manifests itself as if the sub-band band-pass is direction dependent. To solve this, the bordering 80~kHz on both sides of a 1.28~MHz subband are normally flagged by \textsc{cotter}. This implies that in normal observations, 13\% of the data are lost due to the poly-phase filter. However, while 80~kHz is sufficient to prevent imaging artefacts, we noticed that the RFI statistics were still slightly biased by the edge channels. Therefore, for the analyses in this paper we increase the removed bandwidth to 200~kHz on either side of each 1.28~MHz sub-band, or 32\% in total.
\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/rfi-per-band}
\caption{RFI occupancy per subband, calculated over all observation nights except GLEAM 2014-03-17. The latter has been left out because it is affected by DTV. The horizontal gray line represents the false-positives rate of the RFI detection.}
\label{fig:rfi-per-band}
\end{center}
\end{figure*}

>>>>

The poly-phase filter bank that performs the first separation into sub-bands, introduces a 1.28~MHz periodic spectral signature, which is shown in Fig.~\ref{fig:bandpass}. The poly-phase filter band-pass shape is hard to remove completely, because of aliasing each sub-band is affected by leakage from signals in its adjacent sub-bands. The leakage from adjacent sub-bands manifests itself as if the sub-band band-pass is direction dependent. To solve this, the bordering 80~kHz on both sides of a 1.28~MHz subband are normally flagged by \textsc{cotter}. This implies that in normal observations, 13\% of the data are lost due to the poly-phase filter. However, while 80~kHz is sufficient to prevent imaging artefacts, we noticed that the RFI statistics were still slightly biased by the edge channels. In particular, the detected fraction of RFI over frequency is about 0.5\% higher in the edge channels. Therefore, for the analyses in this paper we increase the removed bandwidth to 200~kHz on either side of each 1.28~MHz sub-band, or 32\% in total.
\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/rfi-per-band}
\caption{RFI occupancy per subband, calculated over all observation nights except GLEAM 2014-03-17. The latter has been left out because it is affected by DTV. The horizontal gray line represents the false-positives rate of the RFI detection.}
\label{fig:rfi-per-band}
\end{center}
\end{figure*}
